---
title: "Camera Dataset for CSE4202 Data Mining & Visualization"
author: "Farnaz Baksh"
date: "5/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Import Libraries
``` {r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(dplyr)
```

##Load Dataset & preview
``` {r}
data<-read.csv("/Users/Dell/Desktop/DMViz Assigment/camera_dataset.csv")
head(data)
```

#### Dimension of the Dataset
``` {r}
dimension<-dim(data)
cat("The dimension of the dataset is:", dimension)
```

#### Summary of the Dataset
```{r}
summary(data)
```



##Question 1: Most Popular Year for Camera Release (in our Dataset)
``` {r}
Year <- table(data$Release.date)
barplot(Year,
        main ="Bar Plot of Most Popular Year for Camera Release",
        xlab="Years",
        col = "#5dbcd2")
```

##Question 2: Has there been an increase in Max Resolution over the years?
``` {r}
plot(data$Release.date, data$Max.resolution, 
     main ="Scatter Plot of Max Resolution over the Years",
     pch = 20,
     cex=1.5,
     col="#1979a9",
     ylab = "Resolution",
     xlab = "Year")
```


##Question 3: Describe the relationship between Dimension and Year 
``` {r}
plot(data$Release.date, data$Dimensions, 
     main ="???",
     pch = 20,
     cex=1.8,
     col="#e07b39",
     ylab = "Dimension",
     xlab = "Year")
```

##Question 4: What is the Max Resolution among the models
``` {r}
hist(data$Max.resolution,
     main = "Histogram of Max Resolution",
     xlab="Max Resolution",
     col = "#cce7e8")
```


##Question ?: Has the weight of a camera increase over the years?

##Question ?: Correlation between Normal and Macro Focus Range


##Question ?: Has storage increase over the years?

##Question ?: Did Canon Powershot prices increase?

##Question ?: The relationship between weight and dimension?

##Question ?: Does Weight affect Price?


##Question 10: Which property influence price the most?


##Question 11: What is the prices of Cameras with Max Resolution more than 2000

```{r}
#filter the data set  to extract observations where max resolution is greater than 2000
filtered_maxRes<-data%>%
  filter(Max.resolution>2000)
filtered_maxRes
```


```{r}
ggplot(data, aes(x=filtered_maxRes)) +
         geom_dotplot(dotsize=0.2)
```




##Scatterplot
```{r}
ggplot(data, aes(x = Max.resolution, y = Price)) +
  geom_point()
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(data$Storage.included, data$Weight..inc..batteries.)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
