---
title: "Camera Dataset for CSE4202 Data Mining & Visualization"
author: "Farnaz Baksh"
date: "5/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Import Libraries
``` {r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(dplyr)
```

##Load Dataset & preview
``` {r}
data<-read.csv("/Users/Dell/Desktop/DataMining-Visualization/camera_dataset.csv")
head(data)
```

#### Dimension of the Dataset
``` {r}
dimension<-dim(data)
cat("The dimension of the dataset is:", dimension)
```

#### Summary of the Dataset | General Statistical Operation of the Dataset
```{r}
summary(data)
```

#### Summary of the Sub-Dataset of Variables we used in this Analysis
```{r}
sub_data<- data[, c(1:5, 9:14)]

dimension<-dim(sub_data)
cat("The dimension of the dataset is:", dimension, "\n", "\n")

summary(sub_data)
```


##Question 1: Which year had the most camera releases?
``` {r}
Year <- table(data$Release.date)
barplot(Year,
        main ="Bar Plot showing Most Popular Year for Camera Release",
        xlab="Years",
        col = "#5dbcd2")
```
###Output for Question 1: Which year had the most camera releases?
Based on our dataset, we can see a steadily increase in the amount of camera production over the years. Most of the cameras went on sale in the years; 2004, 2006 and 2007. At the beginning of the year 2001, it can be seen that the camera production has doubled onwards.   


##Question 2: Has there been an increase in Max Resolution over the years?
``` {r}
plot(data$Release.date, data$Max.resolution, 
     main ="Scatter Plot of Max Resolution over the Years",
     pch = 20,
     cex=1.5,
     col="#1979a9",
     ylab = "Resolution",
     xlab = "Year")
```
###Output for Question 2: Has there been an increase in Max Resolution over the years?
The visualization plot shows a steadily increase in the camera's max resolution over the period of 1996-2007. From the year 2000, resolution has entered in the 3000 dimensions in pixels. Then from 2002, the dimensions increased by another 1000 pixels. 


##Question 3: Has there been a decrease in Low Resolution over the years?
``` {r}
plot(data$Release.date, data$Low.resolution, 
     main ="Scatter Plot of Low Resolution over the Years",
     pch = 20,
     cex=1.5,
     col="#39b38e",
     ylab = "Resolution",
     xlab = "Year")
```
###Output for Question 3: Has there been an decrease in Low Resolution over the years?
In a contradictory conclusion, there has been an increase rather than a decrease in low resolution over the years. This means that prior to 2001, the lowest resolution was approximately 500 pixels and then in 2007, the lowest was around 1000 resolution.


##Question 4: Is there any relationship between Dimension and Year?
``` {r}
plot(data$Release.date, data$Dimensions, 
     main ="Scatter Plot: Relationship between Dimension and Year",
     pch = 25,
     cex=1.8,
     col="#552b82",
     ylab = "Dimension",
     xlab = "Year")
```
###Output for Question 4: Is there any relationship between Dimension and Year?
It is evident from our scatter plot that most cameras has a dimension between 80 to 120 from 2000 onwards. Based on our dataset, we can conclude that camera models of Canon Powershot, Fujifilm FinePix and Nikon Coolpix falls most popularly in these dimensions.


##Question 5: What is the is the most popular storage size for cameras?
``` {r}
hist(data$Storage.included,
     main = "Histogram of Storage",
     xlab="Storage",
     breaks = 30,
     col = "#cce7e8")
```
###Output for Question 5: What is the most popular storage size for cameras?
From the year 1996 to 2007, the most popular storage size from our cameras dataset is 16GB. The runner up storage included for our cameras are 32GB and 8GB. 


##Question 6: What is the average price for a Canon Powershot camera?
``` {r}
ggplot(data, aes( x=Price, y=Brand == "1")) +
  geom_boxplot(color="#6e4d00", fill="#e6c26e") + ylab("Brand: Canon Powershot") + ggtitle("Boxplot showing Price for Canon Powershot")+ theme(plot.title = element_text(hjust = 0.5))
```
###Output for Question 6: What is the average price for a Canon PowerShot camera?
Based on the box plot diagram, the average price for a Canon PowerShot camera falls below $500. The FALSE value shows the prices for the other brands (i.e. Fujifilm FinePix and Nikon Coolpix) which shows some outliers.



##Question 7: What is the weight distribution of the cameras over the period of time?
``` {r}
Year <- table(data$Release.date, data$Weight..inc..batteries.)
#Year
ggplot(data, aes(x=Release.date, y=Weight..inc..batteries.)) + 
  geom_point(color='darkblue')+
  geom_smooth(method=lm, se=FALSE) +ylab("Weight")+ xlab("Year") + ggtitle("Weight Distribution")+ theme(plot.title = element_text(hjust = 0.5))

```
###Output for Question 7: What is the weight distribution of the cameras over the period of time?
The diagram shows that there has been a decline in camera weight from the years 1996 to 2007. The slope depicts a fall in the data visualization diagram. 


##Question 8: Which brand has the widest variety of affordable camera models? [Based on our Dataset]
``` {r}
hist(data$Price [data$Brand =="1"],
     main ="Prices for Canon PowerShot",
     col = "#fad67a",
     xlab = "Price")

hist(data$Price [data$Brand =="2"],
     main = "Prices for Fujifilm FinePix",
     col = "#cfa744",
     xlab = "Price")

hist(data$Price [data$Brand =="3"],
     main = "Prices for Nikon Coolpix",
     col = "#fad473",
     xlab = "Price")

```
###Output for Question 8: Which camera brand has the most affordable variety of models? (based on our dataset)
Based on the visualization, it can be seen that most Canon PowerShot models falls in the price range of 100-150. Whereas for the Nikon Coolpix models, the prices fall between 200-250. However for the Fujifilm FinePix, thef=re seems to be many outliers, thus it is hard to determine a narrow range for the prices. It can be shown that most camera prices for Fujifilm FinePix falls below 250. In conclusion, the widest variety of the cheapest camera cost is the Canon PowerShot. 



##Question 9: What are the prices of Cameras with Max Resolution more than 4000 pixels?
```{r}
#filter the dataset  to extract observations where max resolution is greater than 4000
filtered_maxRes<-data%>%
  filter(Max.resolution>4000)
filtered_maxRes[, c(1:2,4, 14)]

ggplot(filtered_maxRes, aes(x = Price, fill = Max.resolution)) + 
  geom_bar(position = "dodge", fill="#c07bed") + ggtitle("Barplot showing Max Resolution > 4000")+ theme(plot.title = element_text(hjust = 0.5))

```
###Output for Question 9: What are the prices of Cameras with Max Resolution more than 4000 pixels?
The barplot shows that one could obtain four cameras in the price range of 1500-1800. Four other cameras are also available in the price range of 150-250.
This is ideal for persons who wants large file formats so that they can manipulate their images in post edits.


##Question 10: Is there Correlation between Normal and Macro Focus Range?
```{r}

#ggplot(data, mapping = aes(x = Normal.focus.range, y = Macro.focus.range, fill = "Abundance")) +
#  geom_tile() + xlab(label = "Normal Focus Range")

ggplot(data, mapping = aes(x = Normal.focus.range, y = Macro.focus.range)) +
  geom_tile(fill ="#e86b84") + xlab(label = "Normal Focus Range") + ylab(label = "Macro Focus Range") + ggtitle("Heatmap showing the relation between Focus Range") + theme(plot.title = element_text(hjust = 0.5))

```
###Output for Question 10: Is there a correlation between Normal and Macro Focus Range?
Most cameras in our dataset has a normal focus distance that ranges between 25-75 and a Macro Focus range that is centered around 1-15. This range signifies how far away or how close someone can be with the camera to take clear and in-focus shots.



