---
title: "Camera Dataset for CSE4202 Data Mining & Visualization"
author: "Farnaz Baksh"
date: "5/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Import Libraries
``` {r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(dplyr)
```

##Load Dataset & preview
``` {r}
data<-read.csv("/Users/Dell/Desktop/DataMining-Visualization/camera_dataset.csv")
head(data)
```

#### Dimension of the Dataset
``` {r}
dimension<-dim(data)
cat("The dimension of the dataset is:", dimension)
```

#### Summary of the Dataset | General Statistical Operation of the Dataset
```{r}
summary(data)
```


##Question 1: Most Popular Year for Camera Release (in our Dataset)
``` {r}
Year <- table(data$Release.date)
barplot(Year,
        main ="Bar Plot showing Most Popular Year for Camera Release",
        xlab="Years",
        col = "#5dbcd2")
```

##Question 2: Has there been an increase in Max Resolution over the years?
``` {r}
plot(data$Release.date, data$Max.resolution, 
     main ="Scatter Plot of Max Resolution over the Years",
     pch = 20,
     cex=1.5,
     col="#1979a9",
     ylab = "Resolution",
     xlab = "Year")
```


##Question 3: Describe the relationship between Dimension and Year 
``` {r}
plot(data$Release.date, data$Dimensions, 
     main ="???",
     pch = 20,
     cex=1.8,
     col="#e07b39",
     ylab = "Dimension",
     xlab = "Year")
```


##Question 4: What is the Max Resolution among the models
``` {r}
hist(data$Max.resolution,
     main = "Histogram of Max Resolution",
     xlab="Max Resolution",
     col = "#cce7e8")
```


##Question 5: Has the weight of a camera increase over the years?
``` {r}
plot(data$Release.date, data$Weight..inc..batteries., 
     main ="Scatter Plot showing Weight of Camera over the Years",
     pch = 20,
     cex=1.5,
     col="#800000",
     ylab = "Weight",
     xlab = "Year")
```

```{r}
ggplot(data, aes(x = Release.date, y = Weight..inc..batteries.)) + geom_point() + ylab("Weight") + xlab("Year")

```


###Brand & Prices
``` {r}
Brand<-table(data$Brand, data$Price)
Brand
hist(data$Brand,
     main = "???",
     xlab="Brand",
     col = "#cce7e8")
```

``` {r}
CanonData<-table(data$Brand =="1")

FujiData<-table(data$Brand == "2")

NikonData<-table(data$Brand == "3")

#BrandData<-table(CanonData,FujiData,NikonData)
#BrandData
```


ggplot(data, aes(x = Brand,  y = Price)) + 
  geom_boxplot() + ylab("Price") + xlab("Brand") +
  ggtitle("Title")

```{r}
CanonData<-table(data$Brand =="1", data$Model)
CanonData
```

##Question ?: Correlation between Normal and Macro Focus Range
```{r}
ggplot(data.aes(y= ))

```

##Question ?: Has storage increase over the years?
``` {r}
Storage_Price <- table(data$Release.date, data$Storage.included)

ggplot(data, aes(x=Storage_Price)) +
  geom_histogram()
```

##Question ?: Did Canon Powershot prices increase?


``` {r}
CanonDataPrice<-data[c(0:97), c(1, 14)]
#CanonDataPrice

#ggplot(data, aes(x = CanonDataPrice)) + 
#  geom_boxplot() + ylab("Price") + xlab("Brand") +
#  ggtitle("Title")

#hist(data$Price[data$Brand =="3" & data$Price],
#     main="Title")
```

##Comparing Prices of the Camera Brands
``` {r}
hist(data$Price [data$Brand =="1"],
     main ="Prices for Canon PowerShot",
     breaks= 2)

hist(data$Price [data$Brand =="2"],
     main = "Prices for Fujifilm FinePix",
     breaks= 3)

hist(data$Price [data$Brand =="3"],
     main = "Prices for Nikon Coolpix",
     breaks= 3)
```

### Price for a 16GB in 2007
``` {r}
input<- data[, c('Dimensions', 'Price')]
#print(input)
hist(input)
```

##Question ?: Most afforable camera?
##Question ?" Most expensive camera?

##Question ?: The relationship between weight and dimension?

##Question ?: Does Weight affect Price?


##Question 10: Which property influence price the most?


##Question 11: What is the prices of Cameras with Max Resolution more than 2000

```{r}
#filter the data set  to extract observations where max resolution is greater than 2000
filtered_maxRes<-data%>%
  filter(Max.resolution>2000)
filtered_maxRes
```


```{r}
ggplot(data, aes(x=filtered_maxRes)) +
         geom_dotplot(dotsize=0.2)
```




##Scatterplot
```{r}
ggplot(data, aes(x = Max.resolution, y = Price)) +
  geom_point()
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(data$Storage.included, data$Weight..inc..batteries.)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
